Long range correlations and their event scale dependence in high multiplicity pp collisions at $\sqrt{s}$ =13 TeV

### 2020-05-26 sec_ana.tex
finish of the section 2

Charged particles are reconstructed by the ITS and TPC, which are working in a constant solenoidal magnetic field of 0.5~T.  The ITS is composed of three sub-systems, Silicon Pixel Detector(SPD), Silicon Drift Detector (SDD) and Silicon Strip Detector (SSD). The ITS and TPC have acceptances up to $|\eta| < 1.4$ and 0.9, respectively, for detection of charged particles with a primary vertex in $|z_\mathrm{vtx}|<10$~cm. The tracking of charged particles is done with the combined information of the ITS and TPC that enables the reconstruction of tracks down to 0.2~GeV/$c$ with a $\sim $75\% efficiency.

The multiplicity class used in the present analysis is top 0-0.1\%, which denotes the most particle-abundant events including  $\sim$31 charged particles in the mid-rapidity region($|\eta|<$0.5). This analysis uses charged particles, whose reconstructed transverse momenta are larger than 0.2 GeV/\it{c}\rm{} in a fiducial region as $|\eta|<$0.9.

>>>>

Charged particles are reconstructed by the ITS and TPC, which are working in a constant solenoidal magnetic field of 0.5~T.  The ITS is composed of three sub-systems, Silicon Pixel Detector(SPD), Silicon Drift Detector (SDD) and Silicon Strip Detector (SSD). The ITS and TPC covering the full azimuthal region have acceptances up to $|\eta| < 1.4$ and 0.9, respectively, for detection of charged particles with a primary vertex in $|z_\mathrm{vtx}|<10$~cm. The tracking of charged particles is done with the combined information of the ITS and TPC that enables the reconstruction of tracks down to 0.2~GeV/$c$ with a $\sim $75\% efficiency.

%The multiplicity class is classified by the signal amplitude of the V0 detector.
The multiplicity class used in the present analysis is the top 0.1\% signal amplitude events by the V0 detector for the set of minimum bias events at ALICE. Corresponding number of charged particles is reported as $\sim$31 in the mid-rapidity region ($|\eta|<0.5$) that is almost 5 times larger than the minimum-bias events.  Statistics of the high multiplicity event benefits from a dedicated high multiplicity trigger that was recently implemented at ALICE  in the LHC Run 2 period.
